MSstatsPTM statistical relative quantification of post-translational modifications in bottom-up proteomic experiments

### 2022-03-16 main/MSstatsPTM_Main.tex
Small

\todo{Would it be possible to re-organize this section? (1) Overview, including the data structures and the figure; (2) Existing methods: limma and t-test, including the description in the notation of the figure; also Isobar-PTM - can express in the same notation? Ok if not; (3) Existing methods: MSstats. Not applicable for PTM but useful background; (4) Proposed approach in the notation of the figure. I feel that the experimental design in Suppler is redundant. Could we fold it into the main text as well?} \todo{In this way, the entire Suppler Sec 2 will be merged into main \; the only methods in supplementary will be the table }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{The proposed approach corrects for high FDR in computer simulations}

>>>>

\todo{Would it be possible to re-organize this section? (1) Overview, including the data structures  the figure and the notation - essentially the section that describes Fig 1; (2) Existing methods: limma and t-test, including the description in the notation of the figure; also Isobar-PTM - can express in the same notation? Ok if not; (3) Existing methods: MSstats. Not applicable for PTM but useful background; (4) Proposed approach in the notation of the figure. I feel that the experimental design in Suppler is redundant. Could we fold it into the main text as well?} \todo{In this way, the entire Suppler Sec 2 will be merged into main \; the only methods in supplementary will be the table }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{The proposed approach corrects \todo{starting here, put all the section titles in past tense} for high FDR in computer simulations}
